The Calculus of Linear Constructions

### 2021-12-03 writing/draft5/draft5.tex
draft

We further extend CLC with rules for defining inductive linear types in the style of CIC, forming the Calculus of Inductive Linear Constructions (CILC). Linear connectives such a $\otimes$ and $\oplus$ are definable using this generalized mechanism in a straightforward way. Through examples, we show that CILC facilitates correct by construction imperative programming and lightweight protocol enforcement.

We have formalized all major results in Coq, and implemented a prototype in OCaml, both of which are available in the first author's Github repository.

>>>>

We further extend CLC with rules for defining inductive linear types in the style of CIC, forming the Calculus of Inductive Linear Constructions (CILC). Linear connectives such a $\otimes$ and $\oplus$ are definable using this generalized mechanism in a straightforward way. Through examples, we show that CILC facilitates lightweight reasoning about stateful programs and protocol enforcement.

We have formalized all major results in Coq and implemented a prototype in OCaml, both of which are available in the first author's Github repository.
